Modi normali di oscillazione del Sole (Presentazione)

### 2017-06-16 MSS.tex
cf
mf

@@

La forza netta dovuta agli urti \'e:
\begin{align}
&\vec{R}_{ij}=\int m\vec{v}C(f_i,f_j)\,d^3v_i\label{eq:friction}\\
&\vec{R}_{ij}=n_in_j\mu_{ij}\alpha_{ij}\vec{V}_{ij}\label{eq:resistance}\\
&\alpha_{ij}=\frac{\mu_{ij}}{KT}\int v_r^3\sigma^Tf^{(0)}(\vec{v_r})\,d^3v_r\label{eq:collisionintegral}\\
&\sigma^T=\int(1-\cos{\chi})\,d\sigma\label{eq:sigmatransport}
\end{align}

>>>>

\begin{frame}{Trasferimento impilso nelle colliioni}

@@

La forza netta dovuta agli urti \'e:
\begin{align}
&\vec{R}_{ij}=\int m\vec{v}C(f_i,f_j)\,d^3v_i%\label{eq:friction}
\vec{R}_{ij}=n_in_j\mu_{ij}\alpha_{ij}\vec{V}_{ij}\label{eq:resistance}\\
&\alpha_{ij}=\frac{\mu_{ij}}{KT}\int v_r^3\sigma^Tf^{(0)}(\vec{v_r})\,d^3v_r%\label{eq:collisionintegral}
\sigma^T=\int(1-\cos{\chi})\,d\sigma\label{eq:sigmatransport}
\end{align}
